Practical Optional Types for Clojure

### 2015-02-28 related-work.tex
retic

\paragraph{Optional type systems}
\begin{itemize}
  \item Reticulated Python~\cite{Vitousek14}
  \item GradualTalk
  \item Flow
\end{itemize}

>>>>

\paragraph{Optional type systems}
Reticulated Python~\cite{Vitousek14} is a gradually typed
system for Python, implemented as a source-to-source
translation that inserts dynamic checks at language boundaries
and supporting Python's first-class object system.
Typed Clojure is implemented as a syntactic check on Clojure
code with no option to insert dynamic checks automatically.
Typed Clojure does not support a first-class object system
because Java has nominal classes, however HMaps offer a subset 
of the structural features offered by Reticulated.

  \item GradualTalk
  \item Flow
\end{itemize}
